---
title: "How to Use wakatimer"
author: "Shinya Uryu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, eval = TRUE, message = FALSE}
library(wakatimer)
```

## Setup (recommend)

1. [Create WakaTime accont](https://wakatime.com/signup).
2. Configure your own [API key](https://wakatime.com/settings).
3. [Registry application](https://wakatime.com/apps) and to get an OAuth 2.0 client token to use wakatimer.

```{r, eval = FALSE, echo = TRUE}
# wakatime api key and app id set to R global environment 
Sys.setenv("WAKATIME_KEY" = "<your api key>")
Sys.setenv("WAKATIME_ID" = "<application id>")
Sys.setenv("WAKATIME_SECRET" = "<application secret>")

# also add to .RProfile
```

```{r, eval = TRUE, echo = FALSE}
key = Sys.getenv("WAKATIME_KEY")
app.id     = Sys.getenv("WAKATIME_ID")
app.secret = Sys.getenv("WAKATIME_SECRET")
```

```{r, eval = FALSE}
# Continue to authorize
write_scope()
```

That's all! **Use like you normally do and your time will record by log.**

```{r, eval = FALSE}
# Normally terminate r session 
q()
```

The **`{wakatimer}`** provide current sessions modificate file information will sent to WakaTime!! Visit https://wakatime.com to see your logged time. However, when in such situation out of scope for post to wakatime API 1) Force Quit RStudio 2) Restart R.

## API Request

```{r, eval = TRUE}
wakatimer:::wt_api(resource = "heartbeats", 
                   key = Sys.getenv("WAKATIME_KEY"), 
                   param = list(date = format(Sys.Date(), "%m/%d/%Y"), time = "time", "entity"))
```

### Send Heartbeat

**`{wakatimer}`** is automatically log and post information that files in project directory when internet connection. Here, I indicate that to sent indivual heartbeat method.

```{r}
# Check recent open files
recent_files()
```


```{r, eval=FALSE}
wakatimer:::check_file_active()
```

[1] "~/git/r_pkg/wakatimer/vignettes/wakatimer-workflow.Rmd"

```{r, eval=FALSE}
# Check condition
file_info()

# $entity
# [1] "~/git/r_pkg/wakatimer/vignettes/wakatimer-workflow.Rmd"
# 
# $type
# [1] "file"
# 
# $time
# [1] 1453720956
# 
# $lines
# [1] 61
# 
# $lineno
# [1] 51
# 
# $cursorpos
# [1] 1
# 
# $project
# [1] "wakatimer"
# 
# $branch
# [1] "master"
# 
# $language
# [1] "Rmd"
# 
# $is_debugging
# [1] FALSE
# 
# $is_write
# [1] FALSE
```



```{r, eval=FALSE}
# Sync individual current active file information to wakatime
wt_sync()
```
